Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
trim related work

% heather - add more results in here since we have more to report. Probably cut down image manipulation?
\begin{abstract}
We introduce Rewind system which assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips. Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed video offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using Rewinds than trips taken alone. Rewind also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

@@

\subsection{Location History}
A project that also leverages location data to capture the essence of a trip is by Thudt et al., who discuss the creation and investigation into the challenges and limits of visual mementos \cite{thudt2016visual}. The authors define visual mementos as ``visualizations of personally relevant data for the purpose of reminiscing, and sharing of life experiences.'' They present one implementation example of visual mementos that involves GPS location histories. This common goal of providing a way for people to reminisce about their trips reinforces the purpose of Rewind. Another reinforcement can be found in the way that their system is enhanced with geotagged photos from Flickr. The three main challenges presented in Thudt et al.'s paper are: 1) evoking familiarity, 2) expressing subjectivity, and 3) obscuring sensitive data. The authors attempt to address those challenges in the tool they built, called Visits, and their findings from the case study show that there is benefit to the visualization of personal mementos. Rewind builds on their work by breaking a trip down into smaller sequences and recreating the visual experience, whereas Visits relies on a more traditional top-down map view and timeline.

Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images. However, Rewind differs in that the mapping is finalized with geolocation data provided by users tracked using smartphones. This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

Other research has used location history not to create a new interface for the user, but for other applications. Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray data from a two-month study involved twenty participants wearing GPS devices. Using geotagged images from Flickr, Becker et al.'s work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}. The data from these studies show each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

Further work in location-based user behavior has been done by Leshed et al. to see how users interpret and interact with spaces differently when using in-car GPS navigation \cite{leshed2008car}. They found that ``the GPS disconnects the drivers from the external environment.'' As a result of the drivers' disengagement with their surroundings, ``the process of interpreting the world, adding value to it, and turning space into place is reduced to a certain extent and drivers remain detached from the indifferent environments that surround them.'' Since Rewind touches on the topic of travel, it also inherently deals with car travel and GPS. We imagine that regular GPS users will interact with Rewinds differently.

A common thing to do with location history data is to develop a visualization of it. Larsen et al. use a spiral chart for a user to see the continuity of their locations, where days are put around the spiral \cite{larsen2013qs}. This visualization allows users to explore and discover patterns in their daily lives. An early implementation of Visits by Thudt et al. focuses on the map and timeline views of location, interleaving them together \cite{thudt2013visits}. In their visualization, users can move from location to location using their pointer, which at the same time moves back and forth in time. This partially inspired the scrubbing technique in Rewind of traveling back and forth in time by scrubbing left and right, at the same time changing the image of what was seen at that time.

Finally, as location reveals where a person was at certain times, and is often a comprehensive view of someone's routes, there are substantial privacy concerns for this type of data. Not only can it reveal a person's home location, but it can also be used to forecast where they might be at a certain time in the future, or where they might not be. Lindqvist et al. \cite{lindqvist2011m} investigate the motivation behind sharing location data, and find that people are sensitive to privacy especially for places frequently visited (like their home). Tang et al. study the feeds of location histories meant for sharing, and discover that users desire different levels of details to be shared with other depending on their relationship with that person \cite{tang2011understanding}. The location itself is often not the concern, but that it is associated with an activity, which is the more sensitive variable. Users also unanimously disliked sharing time-based location, as it was too privacy-invasive. This informed our design of Rewind, where the generated experiences will not specify exactly the location, nor the time it represents. Users have the option to explicitly share a Rewind with another person after reviewing it themselves.

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline

@@

Our study examined episodic processing in metric-specific groups, as well as the performance overall. Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits. Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.

>>>>

% heather - add more results in here since we have more to report. Probably cut down image manipulation?
\begin{abstract}
We introduce \textit{Rewind}, a system that assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips. \textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in \textit{Rewind} are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed \textit{Rewind} videos offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone. \textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

@@

\subsection{Location History}
Silva and Aizawa build on location data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images. However, Rewind differs in that the mapping is finalized with geolocation data provided by users tracked using smartphones. This means that Rewind serves more of a geteway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons. %; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

Larsen et al. use a spiral chart for a user to see the continuity of their locations, where days are placed around the spiral \cite{larsen2013qs}. This visualization allows users to explore and discover patterns in their daily lives. An early implementation of Visits by Thudt et al. focuses on the map and timeline views of location, interleaving them together \cite{thudt2013visits}. In their visualization, users can move from location to location using their pointer, which at the same time moves back and forth in time. This partially inspired the scrubbing technique in Rewind of traveling back and forth in time by scrubbing left and right, at the same time changing the image of what was seen at that time.

Later, Thudt et al. expand on the idea of visual mementos based on location history data and geotagged photos from Flickr~\cite{thudt2016visual}. The authors define visual mementos as ``visualizations of personally relevant data for the purpose of reminiscing, and sharing of life experiences.'' This common goal of providing a way for people to reminisce about their trips reinforces the purpose of Rewind.
% Another reinforcement can be found in the way that their system is enhanced with geotagged photos from Flickr.
The three main challenges presented in Thudt et al.'s paper are: 1) evoking familiarity, 2) expressing subjectivity, and 3) obscuring sensitive data. The authors attempt to address those challenges in Visits, and their findings from the case study show that there is benefit to the visualization of personal mementos. Rewind builds on their work by breaking a trip down into smaller sequences and recreating the visual experience, whereas Visits relies on a more traditional top-down map view and timeline.

% Other research has used location history not to create a new interface for the user, but for other applications.
Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray data from a two-month study involved twenty participants wearing GPS devices. Using geotagged images from Flickr, Becker et al.'s work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests \cite{Becker2015}. The data from these studies show each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

Further work in location-based user behavior has been done by Leshed et al. to see how users interpret and interact with spaces differently when using in-car GPS navigation \cite{leshed2008car}. They found that ``the GPS disconnects the drivers from the external environment.'' As a result of the drivers' disengagement with their surroundings, ``the process of interpreting the world, adding value to it, and turning space into place is reduced to a certain extent and drivers remain detached from the indifferent environments that surround them.'' Since Rewind touches on the topic of travel, it also inherently deals with car travel and GPS. We imagine that regular GPS users will interact with Rewinds differently, and examine this in our study.

Finally, location data reveals where a person was at certain times and the routes they take, so there are substantial privacy concerns. Not only can it reveal a person's home location, but it can also be used to forecast where they might be at a certain time in the future, or where they might not be. Lindqvist et al. \cite{lindqvist2011m} investigate the motivation behind sharing location data, and find that people are sensitive to privacy especially for places frequently visited (like their home). Tang et al. study the feeds of location histories meant for sharing, and discover that users desire different levels of details to be shared with other depending on their relationship with that person \cite{tang2011understanding}. The location itself is often not the concern, but that it is associated with an activity, which is the more sensitive variable. Users also unanimously disliked sharing time-based location, as it was too privacy-invasive. This informed our design of Rewind, where the generated experiences will not specify exactly the location, nor the time it represents. Users have the option to explicitly share a Rewind with another person after reviewing it themselves.

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & \cellcolor[HTML]{FFFFC7}34 & \cellcolor[HTML]{FFFFC7}27 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & \cellcolor[HTML]{FFFFC7}0.71 & \cellcolor[HTML]{FFFFC7}0.89 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & \cellcolor[HTML]{FFFFC7}88 & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}12 & \cellcolor[HTML]{FFFFC7}53 & \cellcolor[HTML]{FFFFC7}49 & \cellcolor[HTML]{FFFFC7}6 & 33 & 58 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 94} & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}5 & \cellcolor[HTML]{FFFFC7}8 & \cellcolor[HTML]{FFFFC7}18 & \cellcolor[HTML]{FFFFC7}70 & \cellcolor[HTML]{FFFFC7}66 & \cellcolor[HTML]{FFFFC7}10 & 46 & 80 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 0.13} & \cellcolor[HTML]{FFFFC7}0.26 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.11 & \cellcolor[HTML]{FFFFC7}0.10 & \cellcolor[HTML]{FFFFC7}0.20 & \cellcolor[HTML]{FFFFC7}0.40 & 0.11 & 0.18 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline

@@

Our study examined episodic processing in metric-specific groups, as well as the performance overall. Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits. Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
